\sc Building sex-specific synthetic lethality network in cancer - Temp Name

### 2023-07-25 sl_report_pmcrc/paper0904.tex
updates

\usepackage{listings}
\usepackage{xcolor}

@@

@@

	Raw count gene expression matrices for males and females were pre-filtered to remove genes unlikely to exhibit differential expression. For each matrix, we calculated the 90th quantile of overall gene expression as a threshold. For each gene in the matrix, we checked to see whether its expression was greater than the threshold in at least 1 sample, and removed genes where no samples showed expression greater than the quantile threshold.

>>>>

\usepackage{listings}
\usepackage{xcolor}
\usepackage{booktabs}
\usepackage{tabulary}

@@

	\begin{table}[ht]
	\centering
	\caption{List of 12 TCGA Cancer Types With Number of Matched Tumor-Normal Samples in Males and Females.}
	% Second version of table, with booktabs.
	\begin{tabulary}{\textwidth}{CCCC}\toprule
		& \multicolumn{3}{c}{TCGA information}
		\\\cmidrule(lr){2-4}
		& Cancer Type  & Matched Female Samples & Matched Male Samples\\\midrule
		& BLCA & 9 & 10 \\
		& COAD & 21 & 20 \\
		& ESCA & 5 & 8 \\
		& HNSC & 14 & 29 \\
		& KICH & 12 & 13 \\
		& KIRC & 20 & 52 \\
		& KIRP & 10 & 22 \\
		& LIHC & 22 & 28 \\
		& LUAD & 34 & 24 \\
		& LUSC & 14 & 37 \\
		& STAD & 10 & 23 \\
		& THCA & 42 & 17 \\
		& \textcolor{red}{TOTAL} & \textcolor{red}{213} & \textcolor{red}{283} \\\bottomrule
	\end{tabulary}
	\end{table}

@@

	Raw count gene expression matrices for males and females were pre-filtered to remove genes unlikely to exhibit differential expression. For each matrix, we calculated the 90th quantile of overall gene expression as a threshold. For each gene in the matrix, we checked to see whether its expression was greater than the threshold in at least 1 sample. We removed genes where no samples showed an expression value greater than the quantile threshold.
